\documentclass{tufte-handout}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{microtype}

\pagestyle{empty}


\title{Gorilla Report}
\author{Evaristo Columby, Martino Secchi, Søren Palmund and Ivan Naumovski}

\begin{document}
  \maketitle

  \section{Results}

  Our implementation produces the expected results on all pairs of species.

  We compared the species in \verb!HbB_FASTAs-in.txt!
  with the common rat, given by

  \begin{verbatim}
  MVHLTDAEKA AVNALWGKVN PDDVGGEALG RLLVVYPWTQ RYFDSFGDLS
  SASAIMGNPK VKAHGKKVIN AFNDGLKHLD NLKGTFAHLS ELHCDKLHVD
  PENFRLLGNM IVIVLGHHLG KEFTPCAQAA FQKVVAGVAS ALAHKYH
  \end{verbatim}

  The closest species to \emph{Rattus rattus} is $[\ldots]$, with the following optimal alignment:\sidenote{Replace with actual alignment between the two species.}

\medskip
  \begin{fullwidth}\small
  \begin{verbatim}
  MVHLTDAEKAAVNALWGKVNPDDV-YGGEAL----VVYPWTQRYFDSFGDLS
  MVHLTDAEKAAVNALWGKVNPDDVX-GGEALGRLLVVYPWTIRYFDSFGDLS

  SASAIMGNPKVKAHGKKVINAFND---KHLDNLKGTFAHLSELHTDKLHVDPENFRLLGN
  SASAIMGNPKVKAHGKKVINAFNDDVHKHLDNLKGTFAHLSELHSDKLHVDPENFRLLGN

  MIVIVLGHHLGKEFTPC----------AQAAFQKVVAGVASALAHKYH
  MIVIVLGHHLGKEFTPCVOLKSWAGENAQAAFQKVVAGVASALAHKYH
  \end{verbatim}
\end{fullwidth}



  \section{Implementation details}
We did a function which compares two strings, we denote these as $X$ and  $Y$.
Initially we do a two-dimensional array, called $M$, which represents the value of a given coordinate within the matching.

\begin{equation}
    opt(X_i, Y_j) = 
    \begin{cases}
    	i\cdot\delta       			& \quad \text{if } j = 0\\
        max 	\begin{cases}	 
        \alpha_{X_i Y_i} + opt(i-1, j-1)\\
        \delta + opt(i-1, j)\\
        \delta + opt(i, j-1)\\
\end{cases}				& \quad \text otherwise \\
        j\cdot\delta	& \quad \text{if } i = 0  \\
    \end{cases}
\end{equation}\newline

We compare every character in $X$ to every character in $Y$.
We have the overhead of using twice quadratic space, M and Path are both two-dimensional arrays which have the length of $X$ as the first dimension and the length of $Y$ as the second dimension. We are aware that we could collapse these arrays to only contain the information we need.
This could make us go from $O(m n) \rightarrow O(m+n)$ in space complexity.

  For two sequences of length $n$ and $m$, respectively, our implementation uses $O((n^3+\log^2 m)\cos n)$ time and
  $O(1)$ space.


\end{document}
