\documentclass{tufte-handout}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{microtype}

\pagestyle{empty}

\title{Stable Matching Report}
\author{Martino Secchi, Søren Palmund and Ivan Naumovski}

\begin{document}
  \maketitle

  \section{Results}

  Our implementation produces the expected results on all small input--
  output file pairs. On the large input--output file pairs we have tested
  some samples.

  \noindent
  On input {\tt sm-bbt-in.txt}, we produce the following matching:
  \begin{quotation}
    Sheldon--Amy, Rajesh--Emily, Howard--Bernadette, Leonard--Penny.
  \end{quotation}
  
  \noindent
  On input {\tt sm-friends-in.txt}, we produce the following matching:
  \begin{quotation}
  	Ross--Rachel, Chandler--Monica, Joey--Phoebe
  \end{quotation}

  \section{Implementation details}

  The input is stored in a raw array where odd numbers are men and even numbers 
  are women. We have created a {\tt Person} class containing the person's preferences 
  as a stack and the inverted preferences (in which the key is the id of another person 
  and the value is the ranked preference).

  We can check to find a free man who has not proposed to every woman in time $O(1)$, 
  because we store the unmatched men in a stack.
  
  \subsection{Run time}

  With these data structures, our implementation runs in time $O(n^2)$ (average) on 
  inputs with $n$ men and $n$ women.

  The best case is $O(n)$ where every man is matched up with his most preferred woman
  and there are no unstable matches. Worst case is the situation where one man is consistently
  matched and later replaced in favor of another man. In this case the run time of our 
  implementation is $O(n^2)$.

  \subsection{Walkthrough}

  \begin{itemize}
  \item Pop a free man
  \item Pop his first preference
  \item Is she matched?
    \begin{itemize}
    \item[] No
    \begin{itemize}
    \item Engage the couple
    \end{itemize}
    \item[] Yes 
      \begin{itemize}
        \item Look up fiancee
        \item Compare the ranking of him and the free man
        \item Push the lesser preferred guy onto stack of free men  
      \end{itemize}
    \end{itemize}
    \item Repeat until there are no free men left
  \end{itemize}

\end{document}
